When are Fuzzy Extractors Possible?

### 2014-10-07 trunk/info-bounds/FuzzyExtPossibility.tex
minor typos

\paragraph{The Case of Known Distribution}
If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.  In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not effect security.}.

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |\beta_{t}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
\end{corollary}

@@

\subsection{Arbitrary Distributions}
The worst-case hashing approach does not work for arbitrary sources.  The reason is that some balls may have  many points but low total weight.  Let $W$ be a distribution, denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$.  Let $B^2_t,..., B^{2^{-\Hoo(W)}}_t$ be balls with one point each with probability $\Pr[W\in B^i_t] = 2^{-\Hoo(W)}$.  Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.  However, with probability $1-2^{-\Hoo(W)}$ the initial reading is outside of $B^1_t$ and the hash completely reveals the point.

>>>>

\paragraph{The Case of Known Distribution}
If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.  In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not affect security.}.

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |\beta_{t}|\cdot n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
\end{corollary}

@@

\subsection{Arbitrary Distributions}
The worst-case hashing approach does not work for arbitrary sources.  The reason is that some balls may have  many points but low total weight. For example, let $W$ be a distribution consisting of the following balls. Denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$.  Let $B^2_t,..., B^{2^{-\Hoo(W)}}_t$ be balls with one point each with probability $\Pr[W\in B^i_t] = 2^{-\Hoo(W)}$.  Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness on $B^1_t$.  However, with probability $1-2^{-\Hoo(W)}$ the initial reading is outside of $B^1_t$, and the hash completely reveals the point.
